This is an example of article title

### 2019-08-29 paper.tex
abs

\begin{abstract}

We present JuliaDB, a distributed database for analytical workloads that is built solely in Julia, a high-level high-performance dynamic language for numerical computing. JuliaDB is designed to allow seamless use of user-defined Julia functions and data types. Julia's just-in-time compilation welds code from across Julia's package ecosystem as well as user code to generate efficient machine code allowing for high-performance data science in a coherent environment. We show example applications involving error analysis, and online statistics. Our benchmark shows that the system can perform on-par with or betters that of pandas and tidyverse in R.
\headingtable

>>>>

\begin{abstract}
We describe how the two-language problem manifests in the world of analytical databases. A system with this problem takes at least two languages to implement: a low-level statically compiled language such as C or C++ to implement the performance-sensitive operations, and a high-level dynamic scripting language such as Python or R to implement the user-facing API. This dichotomy usually exists because the latter language cannot compile to efficient machine code like the former, and the former does not have the ease-of-use as the latter. We present JuliaDB, a distributed database for analytical workloads that is built solely in Julia, and does not have this and other resulting problems. JuliaDB is designed to allow seamless use of user-defined Julia functions and data types. Julia's just-in-time compilation welds code from across Julia's package ecosystem as well as user code to generate efficient machine code allowing for high-performance data science in a coherent environment. We show a case study involving the use of a custom numeric type. Our benchmark shows that the system can perform on-par with or betters that of pandas and tidyverse in the cases we tested.

\headingtable
